Mapping Microblogging Posts to Encyclopedia Articles

### 2011-02-22 lids/twittersearchwrap/paper/paper.tex

Twitter offers the possibility to search for tweets containing a specific term or hash tags. This search returns a fixed number of most recent tweets containing the search term. However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for. As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used. To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms

Why need Wikipedia entities?

Need context/signal to feed wikifier \cite{key:wikifier}.

\section{Method Overview}

@@

\section{Experiments and Evaluation}

@@

%\begin{table}[ht*]
%\centering
%\begin{tabular}{ 1 }
%Search term                    \\
%\hline
%\#s21 \\
%Karlsruhe\\
%\end{tabular}
%\caption{Search terms}\label{tbl:terms}
%\end{table}

>>>>

Twitter offers the possibility to search for tweets containing a specific term or hash tags. This search returns a fixed number of most recent tweets containing the search term. However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for. As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used. To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms, but also serve as a starting point when searching for further information related to the search result. This also helps to determine what the meaning of cryptic hash tags such as $\#s21$ or $\#ka$ mean.

In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities. While it would be more interesting to annotate each single tweet with relevant entities, tweets are too short to contain much relevant information which could be used as input for the annotation tool. Thus, we chose to generate annotations for the whole search result.

The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).

Annotations should be stable over time, unless the topics discussed in the tweets containing the search term change. In nan evaluation of our approach we have tried to analyse the stability of the result.

The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation

\section{Method Overview}
\label{sect:method}

@@

\section{Experiments and Evaluation}
\label{sect:eval}

@@

\begin{table}[ht*]
\centering
\begin{tabular}{ c }
Search term                    \\
\hline
\#s21 \\
Karlsruhe\\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}
